### 2014-11-07 report/preamble.tex
Move some table and plot styles

\newenvironment{wide}{
\pagebreak
\newgeometry{
 top=15mm,
 inner=15mm,
 outer=15mm,
 bottom=15mm,
 headheight=15pt,
 headsep=5mm,
 footnotesep=5mm,
 footskip=10mm}
\begin{landscape}
% Use TiKZ?
% http://tex.stackexchange.com/questions/40501/using-restoregeometry-in-environment-next-page-runs-off-the-page-bottom/40503#40503
\setlength\LTcapwidth{\textwidth} % default: 4in (rather less than \textwidth...)
\setlength\LTleft{0pt}            % default: \parindent
\setlength\LTright{0pt}           % default: \fill
}{
\end{landscape}
\pagebreak
\aftergroup\restoregeometry
}

@@

\usepackage{longtable}
\usepackage{caption}
\usepackage{pgfplotstable}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{array}
\pgfplotsset{compat=1.11}% supress warning

@@

\newcommand{\tsvtablesuperwidedatasets}[4]{
\tsvtablestylewide{#2}
\pgfplotstabletypeset[
columns={#3},force remake=true,every nth row={4[-1]}{after row={\addlinespace[0pt]\midrule\addlinespace[0pt]}},fixed,display columns/0/.style={string type, column type=l},display columns/1/.style={string type, column type=i|},%
% Remove dataset dates.
display columns/0/.append style={string replace*={2014-09-01.}{}},%
display columns/0/.append style={string replace*={2014-08-29.}{}},%
display columns/0/.append style={string replace*={2014-07-23.}{}},%
display columns/0/.append style={string replace*={2014w35.}{}},%
display columns/0/.append style={string replace*={2014-07-10.}{}},%
% Shorten health status datasets.
display columns/0/.append style={string replace*={healthstatus.2013.}{hs.}},%
display columns/0/.append style={string replace*={.domain-registrars}{.registrars}},%
display columns/0/.append style={string replace*={.financial-services}{.financial}},%
display columns/0/.append style={string replace*={.higher-education}{.education}},%
display columns/0/.append style={string replace*={.public-authorities}{.pubauth}},%
% Shorten dataset counts.
display columns/0/.append style={string replace*={100000}{100k}},%
display columns/0/.append style={string replace*={10000}{10k}},%
% Shorten dataset type.
display columns/0/.append style={string replace*={random.}{rnd.}},%
display columns/0/.append style={string replace*={-https-www}{-sw}},%
display columns/0/.append style={string replace*={-https}{-s}},%
display columns/0/.append style={string replace*={-http-www}{-hw}},%
display columns/0/.append style={string replace*={-http}{-h}},%
,#4
]{#1}
}

@@

\pgfplotsset{allDatasetsStackedXbar/.style=
{	
xbar stacked=plus,
enlarge x limits=false,
bar width=6pt,
fill opacity=0.9,
xmin=0,
xmax=1,
xtick={0,.2,.4,.6,.8,1},
minor xtick={.1,.3,.5,.7,.9},
xminorgrids=true,
xmajorgrids=true,
% The number style seems to have stopped working?
xticklabel style={
/pgf/number format/fixed,
/pgf/number format/precision=2
},
ytick=data,
y dir=reverse,
yticklabel pos=right,
symbolic y coords={alexa.2014-09-01.random.10000-http,alexa.2014-09-01.random.10000-http-www,alexa.2014-09-01.random.10000-https,alexa.2014-09-01.random.10000-https-www,alexa.2014-09-01.top.10000-http,alexa.2014-09-01.top.10000-http-www,alexa.2014-09-01.top.10000-https,alexa.2014-09-01.top.10000-https-www,alexa.2014-09-01.top.dk.10000-http,alexa.2014-09-01.top.dk.10000-http-www,alexa.2014-09-01.top.dk.10000-https,alexa.2014-09-01.top.dk.10000-https-www,alexa.2014-09-01.top.se.10000-http,alexa.2014-09-01.top.se.10000-http-www,alexa.2014-09-01.top.se.10000-https,alexa.2014-09-01.top.se.10000-https-www,com.2014-08-29.random.10000-http,com.2014-08-29.random.10000-http-www,com.2014-08-29.random.10000-https,com.2014-08-29.random.10000-https-www,dk.2014-07-23.random.10000-http,dk.2014-07-23.random.10000-http-www,dk.2014-07-23.random.10000-https,dk.2014-07-23.random.10000-https-www,net.2014-08-29.random.10000-http,net.2014-08-29.random.10000-http-www,net.2014-08-29.random.10000-https,net.2014-08-29.random.10000-https-www,reach50.2014w35.se-http,reach50.2014w35.se-http-www,reach50.2014w35.se-https,reach50.2014w35.se-https-www,se.2014-07-10.random.100000-http,se.2014-07-10.random.100000-http-www,se.2014-07-10.random.100000-https,se.2014-07-10.random.100000-https-www,se.healthstatus.2013.counties-http,se.healthstatus.2013.counties-http-www,se.healthstatus.2013.counties-https,se.healthstatus.2013.counties-https-www,se.healthstatus.2013.domain-registrars-http,se.healthstatus.2013.domain-registrars-http-www,se.healthstatus.2013.domain-registrars-https,se.healthstatus.2013.domain-registrars-https-www,se.healthstatus.2013.financial-services-http,se.healthstatus.2013.financial-services-http-www,se.healthstatus.2013.financial-services-https,se.healthstatus.2013.financial-services-https-www,se.healthstatus.2013.gocs-http,se.healthstatus.2013.gocs-http-www,se.healthstatus.2013.gocs-https,se.healthstatus.2013.gocs-https-www,se.healthstatus.2013.higher-education-http,se.healthstatus.2013.higher-education-http-www,se.healthstatus.2013.higher-education-https,se.healthstatus.2013.higher-education-https-www,se.healthstatus.2013.isps-http,se.healthstatus.2013.isps-http-www,se.healthstatus.2013.isps-https,se.healthstatus.2013.isps-https-www,se.healthstatus.2013.media-http,se.healthstatus.2013.media-http-www,se.healthstatus.2013.media-https,se.healthstatus.2013.media-https-www,se.healthstatus.2013.municipalities-http,se.healthstatus.2013.municipalities-http-www,se.healthstatus.2013.municipalities-https,se.healthstatus.2013.municipalities-https-www,se.healthstatus.2013.public-authorities-http,se.healthstatus.2013.public-authorities-http-www,se.healthstatus.2013.public-authorities-https,se.healthstatus.2013.public-authorities-https-www},
legend image code/.code={%
\draw[#1] (0pt,-4pt) rectangle (8pt,4pt);
},
},
allDatasetsStackedXbarFullPage/.style=
{	
enlarge y limits=0.006,
width=.6\textwidth,
height=1.4\textwidth,
font=\small
}
}

>>>>

\newenvironment{wide}{
\pagebreak
\newgeometry{
 top=15mm,
 inner=15mm,
 outer=15mm,
 bottom=15mm,
 headheight=15pt,
 headsep=5mm,
 footnotesep=5mm,
 footskip=10mm}
\begin{landscape}
% Use TiKZ?
% http://tex.stackexchange.com/questions/40501/using-restoregeometry-in-environment-next-page-runs-off-the-page-bottom/40503#40503
\setlength\LTleft{0pt}            % default: \fill
\setlength\LTright{0pt}           % default: \fill
}{
\end{landscape}
\pagebreak
\aftergroup\restoregeometry
}

@@

\usepackage{longtable}
\setlength\LTcapwidth{\textwidth} % default: 4in (rather less than \textwidth...)

\usepackage{caption}
\usepackage{pgfplotstable}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{array}
\pgfplotsset{compat=1.11}% supress warning

@@

\newcommand{\tsvtablesuperwidedatasets}[4]{
\tsvtablestylewide{#2}
\pgfplotstabletypeset[
columns={#3},every nth row={4[-1]}{after row={\addlinespace[0pt]\midrule\addlinespace[0pt]}},fixed,display columns/0/.style={string type, column type=l},display columns/1/.style={string type, column type=i|},%
% Remove dataset dates.
display columns/0/.append style={string replace*={2014-09-01.}{}},%
display columns/0/.append style={string replace*={2014-08-29.}{}},%
display columns/0/.append style={string replace*={2014-07-23.}{}},%
display columns/0/.append style={string replace*={2014w35.}{}},%
display columns/0/.append style={string replace*={2014-07-10.}{}},%
% Shorten health status datasets.
display columns/0/.append style={string replace*={healthstatus.2013.}{hs.}},%
display columns/0/.append style={string replace*={.domain-registrars}{.registrars}},%
display columns/0/.append style={string replace*={.financial-services}{.financial}},%
display columns/0/.append style={string replace*={.higher-education}{.education}},%
display columns/0/.append style={string replace*={.public-authorities}{.pubauth}},%
% Shorten dataset counts.
display columns/0/.append style={string replace*={100000}{100k}},%
display columns/0/.append style={string replace*={10000}{10k}},%
% Shorten dataset type.
display columns/0/.append style={string replace*={random.}{rnd.}},%
display columns/0/.append style={string replace*={-https-www}{-sw}},%
display columns/0/.append style={string replace*={-https}{-s}},%
display columns/0/.append style={string replace*={-http-www}{-hw}},%
display columns/0/.append style={string replace*={-http}{-h}},%
,#4
]{#1}
}

@@

\pgfplotsset{allDatasetsStackedXbar/.style=
{	
xbar stacked=plus,
enlarge x limits=false,
bar width=6pt,
fill opacity=0.9,
xmin=0,
xmax=1,
xtick={0,.2,.4,.6,.8,1},
minor xtick={.1,.3,.5,.7,.9},
xminorgrids=true,
xmajorgrids=true,
ytick=data,
y dir=reverse,
yticklabel pos=right,
symbolic y coords={alexa.2014-09-01.random.10000-http,alexa.2014-09-01.random.10000-http-www,alexa.2014-09-01.random.10000-https,alexa.2014-09-01.random.10000-https-www,alexa.2014-09-01.top.10000-http,alexa.2014-09-01.top.10000-http-www,alexa.2014-09-01.top.10000-https,alexa.2014-09-01.top.10000-https-www,alexa.2014-09-01.top.dk.10000-http,alexa.2014-09-01.top.dk.10000-http-www,alexa.2014-09-01.top.dk.10000-https,alexa.2014-09-01.top.dk.10000-https-www,alexa.2014-09-01.top.se.10000-http,alexa.2014-09-01.top.se.10000-http-www,alexa.2014-09-01.top.se.10000-https,alexa.2014-09-01.top.se.10000-https-www,com.2014-08-29.random.10000-http,com.2014-08-29.random.10000-http-www,com.2014-08-29.random.10000-https,com.2014-08-29.random.10000-https-www,dk.2014-07-23.random.10000-http,dk.2014-07-23.random.10000-http-www,dk.2014-07-23.random.10000-https,dk.2014-07-23.random.10000-https-www,net.2014-08-29.random.10000-http,net.2014-08-29.random.10000-http-www,net.2014-08-29.random.10000-https,net.2014-08-29.random.10000-https-www,reach50.2014w35.se-http,reach50.2014w35.se-http-www,reach50.2014w35.se-https,reach50.2014w35.se-https-www,se.2014-07-10.random.100000-http,se.2014-07-10.random.100000-http-www,se.2014-07-10.random.100000-https,se.2014-07-10.random.100000-https-www,se.healthstatus.2013.counties-http,se.healthstatus.2013.counties-http-www,se.healthstatus.2013.counties-https,se.healthstatus.2013.counties-https-www,se.healthstatus.2013.domain-registrars-http,se.healthstatus.2013.domain-registrars-http-www,se.healthstatus.2013.domain-registrars-https,se.healthstatus.2013.domain-registrars-https-www,se.healthstatus.2013.financial-services-http,se.healthstatus.2013.financial-services-http-www,se.healthstatus.2013.financial-services-https,se.healthstatus.2013.financial-services-https-www,se.healthstatus.2013.gocs-http,se.healthstatus.2013.gocs-http-www,se.healthstatus.2013.gocs-https,se.healthstatus.2013.gocs-https-www,se.healthstatus.2013.higher-education-http,se.healthstatus.2013.higher-education-http-www,se.healthstatus.2013.higher-education-https,se.healthstatus.2013.higher-education-https-www,se.healthstatus.2013.isps-http,se.healthstatus.2013.isps-http-www,se.healthstatus.2013.isps-https,se.healthstatus.2013.isps-https-www,se.healthstatus.2013.media-http,se.healthstatus.2013.media-http-www,se.healthstatus.2013.media-https,se.healthstatus.2013.media-https-www,se.healthstatus.2013.municipalities-http,se.healthstatus.2013.municipalities-http-www,se.healthstatus.2013.municipalities-https,se.healthstatus.2013.municipalities-https-www,se.healthstatus.2013.public-authorities-http,se.healthstatus.2013.public-authorities-http-www,se.healthstatus.2013.public-authorities-https,se.healthstatus.2013.public-authorities-https-www},
legend image code/.code={%
\draw[#1] (0pt,-4pt) rectangle (8pt,4pt);
},
},
allDatasetsStackedXbarFullPage/.style=
{	
enlarge y limits=0.006,
width=.6\textwidth,
height=1.4\textwidth,
font=\small
},
xticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
}
}
